---
title: Project - Data Analytics
subtitle: "Data Visualization and Analysis of Motor Trend Cars"
author: 
  - Ethan
  - Dylan
  - Cara
  - Ryan
  - Rachel

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



## Introduction

About this project :car:

In this project we will cover relationships of different variables using the data collected from Motor Trend US magazine. 

# Data

```{r}
data("mtcars")
```

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

## Summary Statistics

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(mtcars)
```

### Summary Statistics

```{r}
skim(mtcars) %>% 
  select(-n_missing)
```


# Visualization #1

```{r}
car_models <- rownames(mtcars)

ggplot(mtcars, aes(x = reorder(car_models, -qsec), y = qsec)) +
  geom_point(color = "blue") +
  labs(title = "1/4 Mile Times by Car Name",
       x = "Car Name",
       y = "1/4 Mile Time") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```
## Explanation

This scatter plot explores the relationship between the 1/4 mile times, and car names in the "mtcars" dataset. The x-axis is organized based on the 1/4 mile times, with car names reordered accordingly. Each point on the scatter plot is represented in blue, denoting a specific car, and its position along the x-axis corresponds to its 1/4 mile time. The Mercedes 230 has by far the slowest 1/4 mile time and the Ford Pantera L has the fastest with Maserati Bora being a close second. 

# Visualization #2
```{r} 
ggplot(mtcars, aes(x = factor(cyl), y = qsec, fill = factor(cyl))) +
  geom_boxplot(alpha = 0.7) +
  geom_point(position = position_jitter(width = 0.3), color = "black", size = 2) +
  labs(title = "1/4 Mile Time by Number of Cylinders",
       x = "Number of Cylinders",
       y = "1/4 Mile Time",
       fill = "Number of Cylinders") +
  scale_fill_discrete(name = "Number of Cylinders") +
  theme_minimal()

```
## Explanation 

This boxplot explores the relationship between the number of cylinders in car engines and their corresponding 1/4 mile times. Engines with 4 cylinders are filled with the color red, engines with 6 cylinders are filled with the color green, and engines with 8 cylinders are filled with the color blue. As you can see, the relationship between number of cylinders and 1/4 mile times show a negative linear distribution.

# Visualization #3
```{r}
mtcars$cyl <- factor(mtcars$cyl)

ggplot(mtcars, aes(x = wt, y = qsec, color = cyl)) +
  geom_point() +
  labs(title = "Scatter Plot of Quarter Mile Time vs. Weight by Number of Cylinders", 
       x = "Weight (1000 lbs)",
       y = "Quarter Mile Time") +
  scale_color_discrete(name = "Number of Cylinders")

```

## Explanation

This scatter plot explores the relationship between car weight, 1/4 mile times, and the number of cylinders in their engines. It displays weight on the x-axis, 1/4 mile time on the y-axis, and uses point color to denote the number of cylinders (4, 6 and 8). On average, lower number of cylinders in the engine result in less weight and slower 1/4 mile time. The higher number of cylinders in the engine results in having a higher weight and faster 1/4 mile times.

# Visualization #4
```{r}
library(ggplot2)

ggplot(mtcars, aes(x = hp, y = qsec, color = factor(vs))) +
  geom_point(size = 3) +
  labs(title = "Quarter Mile Time by Horsepower and Engine Type",
       x = "Horsepower",
       y = "Quarter Mile Time") +
  scale_color_discrete(name = "Engine Type", labels = c("V-shaped", "Straight")) +
  theme_minimal()

```

## Explanation

This scatter plot explores the relationship between car horsepower, 1/4 mile times, and engine type. The x-axis represents horsepower, the y-axis represents 1/4 mile times, and point color distinguishes between V-shaped and Straight engines. Each point represents an individual car, providing understanding into how horsepower and engine type relate to acceleration performance. On average, V-shaped engines have a higher horsepower and faster 1/4 mile times, whereas Straight engine types have less horsepower and slower 1/4 mile times.
